Computational methods in landscape ecology

### 2024-09-20 Sections/01-introduction.qmd
Update Figure

Here, we introduce recent computational developments in some important topics of landscape ecology including software that implements or is potentially capable of implementing them.
In this context, we are focusing on open-source software and specifically scripting languages such as R, Python, and Julia.
However, we do not provide a systematic literature review, or a general introduction to (computational) landscape ecology.
For a more comprehensive and general introduction to landscape ecology, please see @Turner2015LandscapeEcology, @Gergel2017LearningLandscape, or @With2019EssentialsLandscape.

![Overview of landscape ecology topics for which computational developments are discussed.](Figures/Fig-1.png){width=85%}

>>>>

Here, we introduce recent computational developments in some important topics of landscape ecology including software that implements or is potentially capable of implementing them (Fig. 1).
In this context, we are focusing on open-source software and specifically scripting languages such as R, Python, and Julia.
However, we do not provide a systematic literature review, or a general introduction to (computational) landscape ecology.
For a more comprehensive and general introduction to landscape ecology, please see @Turner2015LandscapeEcology, @Gergel2017LearningLandscape, or @With2019EssentialsLandscape.

![Overview of landscape ecology topics for which computational methods are discussed.](Figures/Fig-1.png){width=100%}
